---
title: "Mini-Project 2"
author: "Your Name Here"
date: "October 31, 2017"
output: html_document
---


## Loading the data

This project is so interesting and relevant to my life!

```{r, include=FALSE}

```

```{r,message=FALSE}
load("house_elections.rda")
load("candidates.rda")
load("committees.rda")
load("contributions.rda")


library(tidyverse)
library(dplyr)

comparison <- contributions %>%
  full_join(candidates,by = "cand_id")
comparison
comparison %>% 
  select(cand_id,cand_ici, entity_type)

require(lubridate)
comparison <- comparison %>%
  mutate(transaction_date= mdy(`transaction_dt`))
glimpse(comparison)



ggplot(data = comparison, aes(x =transaction_date, y = transaction_amt/1000000)) +  
  guides(color = guide_legend("entity type")) +
  geom_point(aes(color = entity_type)) +
  scale_y_continuous("transaction amount/million", labels = scales::dollar) +
  scale_x_date("transaction date")
```


join candidates with contributions by cand_id
compare cand_ici with entity_type
we want to see where the money is coming from for challengers vs incumbents vs open seats CAN = Candidate
CCM = Candidate Committee
COM = Committee
IND = Individual (a person)
ORG = Organization (not a committee and not a person)
PAC = Political Action Committee
PTY = Party Organization


