---
title: "Mini-Project 2"
author: "Your Name Here"
date: "October 31, 2017"
output: html_document
---


## Loading the data

This project is so interesting and relevant to my life!

```{r, include=FALSE}

```

```{r,message=FALSE}
load("candidates.rda")
load("contributions.rda")


library(tidyverse)
library(dplyr)

comparison <- contributions %>%
  full_join(candidates,by = "cand_id")


require(lubridate)
comparison<-comparison%>% 
  select(cand_id,cand_ici, entity_type,transaction_amt,transaction_dt)%>%
  mutate(transaction_date= mdy(`transaction_dt`)) %>%
  filter(transaction_date> "2012-01-01" & transaction_date <"2012-12-31")
comparison$entity_type[comparison$entity_type==""] <-NA


glimpse(comparison)


require(scales)
ggplot(data = comparison, aes(x = entity_type))+ 
  labs(title = "change of transaction amount among between 2010 and 2012 on different entity type")+
  guides(color = guide_legend("entity type")) +
  geom_bar(aes(position= transaction_amt/1000000,fill = entity_type),stats="identity")
```
 +  
  scale_shape_manual(values=10:nlevels(comparison$entity_type)) 
 +
  scale_y_continuous("transaction amount/million", labels = scales::dollar) +
  scale_x_date(labels =  date_format("%Y-%m"), date_breaks = "3 months") + 
  theme(axis.text.x = element_text(angle = 60, hjust = 1))



join candidates with contributions by cand_id
compare cand_ici with entity_type
we want to see where the money is coming from for challengers vs incumbents vs open seats CAN = Candidate
CCM = Candidate Committee
COM = Committee
IND = Individual (a person)
ORG = Organization (not a committee and not a person)
PAC = Political Action Committee
PTY = Party Organization


