---
title: "Mini-Project 2"
author: "Your Name Here"
date: "October 31, 2017"
output: html_document
---


## Loading the data

This project is so interesting and relevant to my life!

```{r,message=FALSE, warning  = FALSE}
load("house_elections.rda")
load("candidates.rda")
load("committees.rda")
load("contributions.rda")
require(scales)
library(tidyverse)
library(dplyr)

contributions <- contributions %>%
  full_join(candidates,by = "cand_id")

contributions1<-contributions %>% 
  select(cand_id,cand_ici, entity_type, transaction_amt, transaction_dt)

require(lubridate)
contributions2<-contributions1 %>%
  mutate(transaction_date= mdy(`transaction_dt`)) %>%
  filter(transaction_date> "2012-01-01" & transaction_date <"2012-12-31")

contributions2$entity_type[contributions2$entity_type==""] <-NA
glimpse(contributions2)

contributions3<-contributions2%>%
  filter(entity_type == c("CCM", "CAN", "COM", "PTY", "IND"))

  m <-ggplot(data = contributions3, aes(x =transaction_date, y = transaction_amt, color = entity_type)) +
    scale_shape_manual(values=8:nlevels(contributions2$entity_type)) + 
    labs(title = "change of transaction amount among between 2010 and 2012 based on entity type")+
    guides(color = guide_legend("entity type")) +
    geom_smooth() +
    facet_wrap(~entity_type)+
    scale_y_continuous("transaction amount", labels=scales::dollar) +
    scale_x_date(date_breaks = "2 months") + 
    theme(axis.text.x = element_text(angle = 60, hjust = 1))
    m
  
  large_entity<-c("ORG","PAC")
 
  
   entity_plot<-function(entities) {
    contributions2 %>%
      filter(entity_type == entities)
   }
   lapply(large_entity,FUN=entity_plot)
   
  plot<-function(entities2){
    ggplot(entity_plot(entities2), aes(x =transaction_date, y = transaction_amt/1000)) +
    labs(title = "change of transaction amount among between 2010 and 2012 based on entity type")+
    guides(color = guide_legend("entity type")) +
    geom_smooth() +
    scale_y_continuous("transaction amount", labels=scales::dollar) +
    scale_x_date(date_breaks = "2 months")
  }
  lapply(large_entity, FUN= plot)
    
```
  

```{r,message=FALSE}
ggplot(data = contributions2, aes(x = entity_type))+ 
  labs(title = "change of transaction amount among between 2010 and 2012 on different entity type")+
  guides(color = guide_legend("entity type")) +
  geom_bar(aes(position= transaction_amt/1000000,fill = entity_type),stats="identity")
```
 +  
  scale_shape_manual(values=10:nlevels(comparison$entity_type)) 
 +
  scale_y_continuous("transaction amount/million", labels = scales::dollar) +
  scale_x_date(labels =  date_format("%Y-%m"), date_breaks = "3 months") + 
  theme(axis.text.x = element_text(angle = 60, hjust = 1))





join candidates with contributions by cand_id
compare cand_ici with entity_type
we want to see where the money is coming from for challengers vs incumbents vs open seats CAN = Candidate
CCM = Candidate Committee
COM = Committee
IND = Individual (a person)
ORG = Organization (not a committee and not a person)
PAC = Political Action Committee
PTY = Party Organization


